---
title: "p8106_stl2137_HW3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ISLR)
```

#Loading in data 

```{r}
data(Weekly)
dat <- Weekly[-8] %>% 
  janitor::clean_names()
```

## Part A
(a) Produce some graphical summaries of the Weekly data.
```{r}
featurePlot(x = dat[, 2:7], 
            y = dat$direction,
            scales = list(x=list(relation="free"), 
                          y=list(relation="free")),
            plot = "density", pch = "|", 
            auto.key = list(columns = 2))
```

## Part B

(b) Use the full data set to perform a logistic regression with Direction as the response and the five Lag variables plus Volume as predictors. Do any of the predictors appear to be statistically significant? If so, which ones?
```{r}
glm_fit <- glm(direction ~ lag1 + lag2 + lag3 + lag4 + lag5 + volume, 
               data = dat, 
               family = binomial)

summary(glm_fit)
```

After running `summary(glm_fit)`, it appears that when $\alpha = 0.05$, only lag2 is a statisically significant predictor. 
